### 2017-01-20 paper3.tex
Made Christine's revisions

\subsection{Stellar feedback}
\subsubsection{Ultraviolet radiation and {\sc Hi} regions}
The characteristic temperature of gas photoionized by UV radiation is
$\sim10^{4}\K$ \citep{Krumholz2009}, far lower than the virial temperature
of all but the smallest galaxies.  For galaxies with halo masses below
$10^9\Msun$, photoheating and photoionization by UV radiation strongly limits star
formation \citep{Efstathiou1992}.  The characteristic sound speed for gas in {\sc Hi}
regions is $\sim10\;\rm{km/s}$, similar to characteristic turbulent velocities
and escape speeds in molecular clouds.  Even large {\sc Hi} regions, such as 30
Doradus, have been observed to have expansion rates of only $25\;\rm{km/s}$
\citep{Chu1994}, significantly less than what is needed to drive even a weak
galactic fountain.  Thus it is doubtful that UV radiation plays much role in
launching galactic-scale outflows.

Simulations by \citet{Dale2012} have shown that {\sc Hi} regions alone are unable to
effectively remove gas from their birth clouds, let alone their galaxies but can
alter their structure.  Thus UV can play a local role in simulations that
resolve molecular clouds.

@@

The virial temperature of haloes with masses of a few $10^{12}\;\Msun$ is
$\sim10^6\K$.  If the wind fluid is cooler than the virial temperature, it will
not be rise buoyantly out of the disc into the CGM.
This suggests SN driven winds become less effective, and may fail to launch
altogether somewhere in the mass range of $\sim10^{12}\;\Msun$. The existence of
a peak in the star formation efficiency at this same mass, as seen in
\citet{Behroozi2013} is strong evidence that this indeed be occurring in nature,
and that some other feedback mechanism begins to dominate at higher masses.
Finding out the if, when and how of this transition is important if we want to
know how larger galaxies quench their star formation, and if SN alone can
explain the low star formation efficiency in galaxies below this mass.

@@

\subsection{Star Formation}
We use a standard Schmidt-law star formation recipe, where the rate is set by
the freefall time of gas and an efficiency $c_*$: \begin{equation} \dot \rho_* =
\frac{c_*\rho}{t_{\rm ff}} = c_*\sqrt{\frac{32G}{\rm 3\pi}}\rho^{3/2} \end{equation} We
used an efficiency of $c_*=0.05$, as was used for the original MUGS simulations
\citep{Stinson2010} and in \citet{Keller2015}.  Star formation is only allowed
to take place in gas which satisfies three criteria: it has a temperature below
$1.5\times10^4\K$, density above $9.6\;\rm{cm^{-3}}$ (the density where
gravitational softening becomes important), and is in a converging flow
($\nabla\cdot \boldsymbol{v} < 0$).  This density threshold is larger than the that used
in \citet{Stinson2010} (which used $0.1\;\rm{cm^{-3}}$, but identical to that
used in \citet{Stinson2013}.  We have used this larger threshold (as
\citealt{Governato2010} recommends) to better capture the effects of clustered
star formation.  Aside from this higher star formation threshold, our star
formation recipe remains unchanged from the original MUGS sample.

@@

Aside from a different star formation density and temperature threshold, the
star formation and feedback recipes used here identical to those used in
\citet{Keller2014}.  One of our sample, g1536, was presented earlier in
\citet{Keller2015}.

\subsection{Comparison to Other Feedback Models}
With $\sim10^{51}\; \rm{erg}$ coupled to the ISM per SN this gives
$1.08\times10^{49}\; \rm{erg}\Msun^{-1}$ for the full stellar population.
Comparing this injection rate to other `modern' feedback methods, we typically
are injecting much less energy (and no momentum, which is generated for us
simply through pressure work and the hydrodynamic solver).  For example, the
Illustris simulations \citep{Vogelsberger2014b} use the \citet{Springel2003} ISM
model, with a \citet{Chabrier2003} IMF, giving a total heating rate of
$1.73\times10^{49}\; \rm{erg}\Msun^{-1}$, which along with the
$1.09\times10^{51}\;\rm{erg}$ per SN injected for the kinetic wind model, gives
a total heating rate from SNII of $3.6\times10^{49}\;\rm{erg}\Msun^{-1}$.  The
kinetic winds have their hydrodynamics decoupled from the surrounding ISM,
ensuring no losses from shock-heating and radiative cooling (see
\citealt{Vogelsberger2013,Vogelsberger2014a} for more details on the Illustris
feedback model).

@@

The general properties of each galaxy at $z=0$ can be found in
Table~\ref{z0_table3}.  $\lambda'$ is the dimensionless spin parameter of the
halo, defined by \citet{Bullock2001} as $\lambda'=J/\sqrt{2GM_{\rm vir}^3R_{\rm vir}}$.
$f_b$ is the baryon fraction of the halo.  $z_{1/2}$ and $z_{\rm lmm}$ are the
redshifts at which the halo reaches half of its final mass, and the redshift of
last major merger respectively.  Major mergers are defined to match
\citet{Stinson2010}, as a merger with a halo containing at least $1/3$ the
stellar mass of the main progenitor.  $M_{\rm vir}$, $M_*$, and $M_{\rm gas}$ are the
masses of the full halo, the stellar component, and the gas component
respectively within the virial radius.  $\rm{SFR_{\rm z=0}}$ is the redshift 0 
SFR, averaged over the previous $100\Myr$.  The virial radius
is defined as the radius around the halo such that the enclosed density is 200
times the critical density ($\rho=200\rho_{\rm crit}$).  While we used the same
definitions for quantities reported in \citet{Stinson2010}, every value reported
here is derived from the new MUGS2 simulations.  We also define a {\it central}
region of the halo, which contains the disc and the majority of the stars within
the halo.  The baryon mass within this region is given as $M_{\rm central}$  This
central region is simply a sphere of radius $0.1R_{\rm vir}$.

@@

The {\sc Hi} column density shown in Fig.~\ref{gas_column3} shows, as was seen in
\citet{Keller2015}, large quantities of extraplanar {\sc Hi} gas, driven up by
outflows from the galaxy disc.  {\sc Hi} gas above the galactic plane has been seen
since \citet{Muller1963}.  \citet{Lockman1984} found similar column densities to
what is seen here to heights of $1.5\kpc$.  High-velocity clouds of relatively
dense ($\sim0.1\; \rm{cm^{-3}}$ gas have also been seen both leaving and
returning to the galaxy \citep{Wakker1997}.  Diffuse {\sc Hi} gas has been observed
out to $\sim300\kpc$ in absorption features of numerous nearby galaxies
\citep{Wakker2009,Prochaska2011}.  \citet{Werk2014} surveyed a number of
galaxies in the COS-haloes survey, and found that typical $L*$ galaxies contain
$\sim5 \times10^{10}\Msun$ of cool gas in their CGM.  The face-on {\sc Hi}
distribution for all but a handful of the unregulated (see the following
section) follow the \citet{Broeils1997} {\sc Hi} mass-size relation, with {\sc Hi} column
densities falling below $1\Msun\pc^{-2}$ at radii of $10-20\kpc$.  This is well
within the intrinsic scatter found in the recent observational study of
\citet{Wang2016}.

\subsection{Stellar Mass Runaway}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time3}
\end{figure}
As can be seen in Fig.~\ref{SMHMR3}, roughly half of these galaxies fall within
the expected $z=0$ stellar mass to halo mass relation (SMHMR).  The grey band
shown in the figure is the $2\sigma$ confidence region in the observed SMHMR
from \citet{Hudson2015}, which used the CFHTLens weak lensing survey to produce
a fully-observational SMHMR, without the uncertainties of the using dark
matter-only simulations that are needed for abundance matching techniques (the
\citet{Hudson2015} SMHMR is consistent with past abundance matching estimates
such as \citet{Behroozi2013} and \citet{Moster2013}).  For the rest of this
paper, we will refer to the galaxies that fall within the $2\sigma$ confidence
interval for the observed SMHMR (i.e. galaxies where stellar feedback prevents
overproduction of stars) as {\it well-regulated}, and the galaxies where stellar
feedback fails to produce the correct SMHMR as {\it unregulated}.  No other
criterion is used for determining which population a galaxy falls into. In
addition to overproducing stars, these unregulated galaxies are qualitatively
redder and more bulge dominated, as can be seen in the mock stellar images of
Fig.~\ref{stellar_image3}.  There appears to be no significant difference in
the redshift of the last major merger between the two populations, strongly
suggesting that the failure of stellar feedback to regulate the galaxies is not
simply a matter of recent or violent merging.  The rotation curves in
Fig.~\ref{rotation_curve3} also show the distinct signature of massive bulges
formed by catastrophic angular momentum loss in the unregulated population.
\citet{vanDenBosch2001} showed that this can arise when gas simply traces the
dark matter distribution, without redistribution or ejection by feedback.  The
strong peaks (as high as $700\kms$ for g4720) come about from the central
concentration of baryons in the galaxy bulge.  Without exception, each of the
well-regulated galaxies shows a flat rotation curve, with no evidence of a
significant bulge component.  This matches the qualitative morphology seen in
Fig.~\ref{stellar_image3}.

Fig.~\ref{stellar_central3} shows that for the well-regulated population, the
stellar mass and central baryonic mass follow an extremely tight linear
relation, with a mean star formation efficiency (simply defined here as the
fraction of central baryons that are in stars) of $38\pm2\%$ over a Hubble time.
For the galaxies that fail to self-regulate, they exhibit a total star formation
efficiency of $70\pm10\%$, converting the majority of the baryons that collapse
on to their disc into stars.  Interestingly, the two populations can be divided
cleanly along the $M_{\rm central}=10^{11}\;\Msun$ or the
$M_*=5\times10^{10}\;\Msun$ axis.  This is clear evidence that what explains
the dichotomy here must involve the accretion (or the failure to remove!)
baryons from the central region of the halo, where the disc resides and stars
are formed.  These relations also help to explain some of the correlations seen
observationally, such as the critical mass of $3\times10^{10}\Msun$ that 
\citet{Kauffmann2003a} found dividing star forming and quenched galaxies in the
SDSS at low redshift.

The gas phase diagram of galaxies in the two populations is remarkably similar,
as can be seen in Fig.~\ref{phase3}.  For a representative pair from each
population, of nearly equal halo mass, gas follows essentially the same
evolutionary path, characteristic of a superbubble-regulated ISM, as was shown in
\citet{Keller2015}.  Gas accretes from the halo,
building up a warm ISM at $T\sim10^4\K$.  Where that gas reaches densities of
$\sim 1\;$cm$^{-3}$, it begins to cool quickly and form stars.  Those stars begin to
explode as SN, and a hot superbubble is formed, with $T>10^7\K$.  As the bubble
grows, it's temperature falls as it both expands adiabatically and evaporates
the cold shell surrounding it.  This hot, buoyant gas leaves the disc, rising
through the CGM and cooling adiabatically as it goes.  What is remarkable here
is just how similar the phase diagrams of these two galaxies are.  The slight
differences are what we would expect from Table~\ref{z0_table3}.  g19195 has
$\sim50\%$ less gas than g24334, and more than 3 times the SFR at $z=0$.  Thus,
there is less total material, especially in the warm and cold phases, and
slightly more of the very hot ($T>5\times10^7\K$) gas (the interiors of very young
superbubbles) as a consequence of the higher SFR.  What is important to take
away from these phase diagrams is that a well-regulated and unregulated galaxy
do not have any real difference in the phase behaviour of their gas.  There is
no runaway cooling, or failure of SN to generate hot gas:  what causes the
unregulated population to runaway is purely an effect of the outflow
effectiveness, which is set by the depth of the potential well.

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR3}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR3}}
    \label{SMHMR_time3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time3}.}
    \label{stellar_central_time3}
\end{figure}

@@

The relatively smooth change in the $M_*-M_{\rm central}$ relation, shown in
Fig.~\ref{stellar_central_time3}, shows that it is in fact the central baryon
mass that is more tightly correlated with the stellar mass than the total halo
mass (in galaxies regulated by SN feedback alone). In fact, it is likely that
some of the more massive galaxies in the well-regulated sample are on their way
to failing, but simply have not yet had enough time by $z=0$ to diverge
significantly from the observed SMHMR.  Once more than $\sim10^{11}\Msun$ of
baryons have accreted to the disc of a galaxy, SN alone appear to be unable to
halt the growth of stellar mass.  At this point, star formation efficiency of
the central disc begins to increase, from $\sim40$ to $\sim70$ per cent, resulting in
the differences seen in the two populations at $z=0$.  This accretion crisis, as
it continues to smaller scales, also explains the rotation profiles of the
unregulated population.  The overcollapse that results in runaway starformation
also builds a massive bulge, producing the peaked rotation curves seen in
Fig.~\ref{rotation_curve3}.

@@

Fig.~\ref{massloading_halo3} suggests exactly that.  The mass loadings appear
roughly constant, at $\eta\sim10$ for most of the mass-range for both
populations, but begin to fall at essentially the same mass, at what appears to
be the same rate.  An even tighter relation is seen in
Fig.~\ref{massloading_central3}, when the relation between the central baryon
mass, rather than just the halo mass, is examined. It appears that for the
$\eta-M_{\rm halo}$ and $\eta-M_{\rm central}$ relation, a broken power-law fit, as
defined below, describes both the regulated and unregulated population.
\begin{equation}
    \eta = 
    \begin{cases}
        \alpha M^\beta  & \quad \text{if } M > M_0 \\
        (\alpha M_0^{\beta-\gamma}) M^\gamma & \quad \text{if } M < M_0 \\
    \end{cases}
    \label{outflow_scaling3}
\end{equation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_central.eps}
    \caption[Mass loadings as a function of disc mass]{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/coldmassloading.eps}
    \caption[Outflow mass loading for cold and hot gas]{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading3}
\end{figure}

Using a simple non-linear least squares fit in the on the parameters $\alpha$,
$\beta$, $\gamma$, and $M_0$, we find that the most likely value for these
parameters are $\alpha=0.9\pm0.5$, $\beta=-0.01\pm0.06$, $\gamma=-1.3\pm0.1$,
$M_{0}=10^{10.0\pm0.1}$ for the $\eta-M_{\rm central}$ relation, and $\alpha=1\pm1$,
$\beta=0.0\pm0.1$, $\gamma=-1.8\pm0.2$, $M_{0}=10^{11.37\pm0.08}$ for the
$\eta-M_{\rm halo}$ relation.  A fit for both of the populations independently is
consistent with these values derived for the full set of MUGS2 galaxies.
Interestingly, {\it neither} of these slopes is consistent with simple energy
or momentum driven winds (although a single power-law fit does give a slope of
$\sim0.5\pm0.2$, consistent with an energy-driven scenario, albeit with a much
weaker fit).  These values are consistent, however, with the constraints derived
for the mass--metallicity relation and gas content in nearby galaxies derived by
\citet{Peeples2011} (namely, that $\alpha$ in the $\eta\propto v_c^{-\alpha}$
relation be steeper than 3).

>>>>

\subsection{Stellar feedback}
\subsubsection{Ultraviolet radiation and {\sc Hii} regions}
The characteristic temperature of gas photoionized by UV radiation is
$\sim10^{4}\K$ \citep{Krumholz2009}, far lower than the virial temperature of
all but the smallest galaxies.  For galaxies with halo masses below $10^9\Msun$,
photoheating and photoionization by UV radiation strongly limits star formation
\citep{Efstathiou1992}.  The characteristic sound speed for gas in {\sc Hii}
regions is $\sim10\;\rm{km/s}$, similar to characteristic turbulent velocities
and escape speeds in molecular clouds.  Even large {\sc Hii} regions, such as 30
Doradus, have been observed to have expansion rates of only $25\;\rm{km/s}$
\citep{Chu1994}, significantly less than what is needed to drive even a weak
galactic fountain.  Thus it is doubtful that UV radiation plays much role in
launching galactic-scale outflows.

Simulations by \citet{Dale2012} have shown that {\sc Hii} regions alone are
unable to effectively remove gas from their birth clouds, let alone their
galaxies but can alter their structure.  Thus UV can play a local role in
simulations that resolve molecular clouds.

@@

The virial temperature of haloes with masses of a few $10^{12}\;\Msun$ is
$\sim10^6\K$.  If the wind fluid is cooler than the virial temperature, it will
not rise buoyantly out of the disc into the CGM.  This suggests SN driven winds
become less effective, and may fail to launch altogether somewhere in the mass
range of $\sim10^{12}\;\Msun$. The existence of a peak in the star formation
efficiency at this same mass, as seen in \citet{Behroozi2013} is strong evidence
that this indeed occurring in nature, and that some other feedback mechanism
begins to dominate at higher masses.  Finding out the if, when and how of this
transition is important if we want to know how larger galaxies quench their star
formation, and if SN alone can explain the low star formation efficiency in
galaxies below this mass.

@@

\subsection{Star Formation}
We use a standard Schmidt-law star formation recipe, where the rate is set by
the freefall time of gas and an efficiency $c_*$: \begin{equation} \dot \rho_* =
\frac{c_*\rho}{t_{\rm ff}} = c_*\sqrt{\frac{32G}{\rm 3\pi}}\rho^{3/2} \end{equation} We
used an efficiency of $c_*=0.05$, as was used for the original MUGS simulations
\citep{Stinson2010} and in \citet{Keller2015}.  Star formation is only allowed
to take place in gas which satisfies three criteria: it has a temperature below
$1.5\times10^4\K$, density above $9.6\;\rm{cm^{-3}}$ (the density where
gravitational softening becomes important), and is in a converging flow
($\nabla\cdot \boldsymbol{v} < 0$).  This density threshold is larger than that used
in \citet{Stinson2010} (which used $0.1\;\rm{cm^{-3}}$), but identical to that
used in \citet{Stinson2013}.  We have used this larger threshold (as
\citealt{Governato2010} recommends) to better capture the effects of clustered
star formation.  Aside from this higher star formation threshold, our star
formation recipe remains unchanged from the original MUGS sample.

@@

Aside from a different star formation density and temperature threshold, the
star formation and feedback recipes used here are identical to those used in
\citet{Keller2014}.  One of our sample, g1536, was presented earlier in
\citet{Keller2015}.

\subsection{Comparison to Other Feedback Models}
With $\sim10^{51}\; \rm{erg}$ coupled to the ISM per SN this gives
$1.08\times10^{49}\; \rm{erg}\;\Msun^{-1}$ for the full stellar population.
Comparing this injection rate to other `modern' feedback methods, we typically
are injecting much less energy (and no momentum, which is generated for us
simply through pressure work and the hydrodynamic solver).  For example, the
Illustris simulations \citep{Vogelsberger2014b} use the \citet{Springel2003} ISM
model, with a \citet{Chabrier2003} IMF, giving a total heating rate of
$1.73\times10^{49}\; \rm{erg}\Msun^{-1}$, which along with the
$1.09\times10^{51}\;\rm{erg}$ per SN injected for the kinetic wind model, gives
a total heating rate from SNII of $3.6\times10^{49}\;\rm{erg}\Msun^{-1}$.  The
kinetic winds have their hydrodynamics decoupled from the surrounding ISM,
ensuring no losses from shock-heating and radiative cooling (see
\citealt{Vogelsberger2013,Vogelsberger2014a} for more details on the Illustris
feedback model).

@@

The general properties of each galaxy at $z=0$ can be found in
Table~\ref{z0_table3}.  $\lambda'$ is the dimensionless spin parameter of the
halo, defined by \citet{Bullock2001} as $\lambda'=J/\sqrt{2GM_{\rm vir}^3R_{\rm vir}}$.
$f_b$ is the baryon fraction of the halo.  $z_{1/2}$ and $z_{\rm lmm}$ are the
redshifts at which the halo reaches half of its final mass, and the redshift of
last major merger respectively.  Major mergers are defined to match
\citet{Stinson2010}, as a merger with a halo containing at least $1/3$ the
stellar mass of the main progenitor.  $M_{\rm vir}$, $M_*$, and $M_{\rm gas}$ are the
masses of the full halo, the stellar component, and the gas component
respectively within the virial radius.  $\rm{SFR_{\rm z=0}}$ is the redshift 0 
SFR, averaged over the previous $100\Myr$.  The virial radius
is defined as the radius around the halo such that the enclosed density is 200
times the critical density ($\rho=200\rho_{\rm crit}$).  While we used the same
definitions for quantities reported in \citet{Stinson2010}, every value reported
here is derived from the new MUGS2 simulations.  We also define a {\it central}
region of the halo, which contains the disc and the majority of the stars within
the halo.  The baryon mass within this region is given as $M_{\rm central}$.  This
central region is simply a sphere of radius $0.1R_{\rm vir}$.

@@

The {\sc Hi} column density shown in Fig.~\ref{gas_column3} shows, as was seen in
\citet{Keller2015}, large quantities of extraplanar {\sc Hi} gas, driven up by
outflows from the galaxy disc.  {\sc Hi} gas above the galactic plane has been seen
since \citet{Muller1963}.  \citet{Lockman1984} found similar column densities to
what is seen here to heights of $1.5\kpc$.  High-velocity clouds of relatively
dense ($\sim0.1\; \rm{cm^{-3}}$) gas have also been seen both leaving and
returning to the galaxy \citep{Wakker1997}.  Diffuse {\sc Hi} gas has been observed
out to $\sim300\kpc$ in absorption features of numerous nearby galaxies
\citep{Wakker2009,Prochaska2011}.  \citet{Werk2014} surveyed a number of
galaxies in the COS-haloes survey, and found that typical $L*$ galaxies contain
$\sim5 \times10^{10}\Msun$ of cool gas in their CGM.  The face-on {\sc Hi}
distribution for all but a handful of the unregulated (see the following
section) follow the \citet{Broeils1997} {\sc Hi} mass-size relation, with {\sc Hi} column
densities falling below $1\Msun\pc^{-2}$ at radii of $10-20\kpc$.  This is well
within the intrinsic scatter found in the recent observational study of
\citet{Wang2016}.

\subsection{Stellar Mass Runaway}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time3}
\end{figure}
As can be seen in Fig.~\ref{SMHMR3}, roughly half of these galaxies fall within
the expected $z=0$ stellar mass to halo mass relation (SMHMR).  The grey band
shown in the figure is the $2\sigma$ confidence region in the observed SMHMR
from \citet{Hudson2015}, which used the CFHTLens weak lensing survey to produce
a fully-observational SMHMR, without the uncertainties from using the dark
matter-only simulations that are needed for abundance matching techniques (the
\citet{Hudson2015} SMHMR is consistent with past abundance matching estimates
such as \citet{Behroozi2013} and \citet{Moster2013}).  For the rest of this
paper, we will refer to the galaxies that fall within the $2\sigma$ confidence
interval for the observed SMHMR (i.e. galaxies where stellar feedback prevents
overproduction of stars) as {\it well-regulated}, and the galaxies where stellar
feedback fails to produce the correct SMHMR as {\it unregulated}.  No other
criterion is used for determining which population a galaxy falls into. In
addition to overproducing stars, these unregulated galaxies are qualitatively
redder and more bulge dominated, as can be seen in the mock stellar images of
Fig.~\ref{stellar_image3}.  There appears to be no significant difference in
the redshift of the last major merger between the two populations, strongly
suggesting that the failure of stellar feedback to regulate the galaxies is not
simply a matter of recent or violent merging.  The rotation curves in
Fig.~\ref{rotation_curve3} also show the distinct signature of massive bulges
formed by catastrophic angular momentum loss in the unregulated population.
\citet{vanDenBosch2001} showed that this can arise when gas simply traces the
dark matter distribution, without redistribution or ejection by feedback.  The
strong peaks (as high as $700\kms$ for g4720) come about from the central
concentration of baryons in the galaxy bulge.  Without exception, each of the
well-regulated galaxies shows a flat rotation curve, with no evidence of a
significant bulge component.  This matches the qualitative morphology seen in
Fig.~\ref{stellar_image3}.

Fig.~\ref{stellar_central3} shows that for the well-regulated population, the
stellar mass and central baryonic mass follow an extremely tight linear
relation, with a mean star formation efficiency (simply defined here as the
fraction of central baryons that are in stars) of $38\pm2\%$ over a Hubble time.
For the galaxies that fail to self-regulate, they exhibit a total star formation
efficiency of $70\pm10\%$, converting the majority of the baryons that collapse
onto their disc into stars.  Interestingly, the two populations can be divided
cleanly along the $M_{\rm central}=10^{11}\;\Msun$ or the
$M_*=5\times10^{10}\;\Msun$ axis.  This is clear evidence that what explains
the dichotomy here must involve the accretion (or the failure to remove!)
baryons from the central region of the halo, where the disc resides and stars
are formed.  These relations also help to explain some of the correlations seen
observationally, such as the critical mass of $3\times10^{10}\Msun$ that 
\citet{Kauffmann2003a} found dividing star forming and quenched galaxies in the
SDSS at low redshift.

The gas phase diagram of galaxies in the two populations is remarkably similar,
as can be seen in Fig.~\ref{phase3}.  For a representative pair from each
population, of nearly equal halo mass, gas follows essentially the same
evolutionary path, characteristic of a superbubble-regulated ISM, as was shown in
\citet{Keller2015}.  Gas accretes from the halo,
building up a warm ISM at $T\sim10^4\K$.  Where that gas reaches densities of
$\sim 1\;$cm$^{-3}$, it begins to cool quickly and form stars.  Those stars begin to
explode as SN, and a hot superbubble is formed, with $T>10^7\K$.  As the bubble
grows, its temperature falls as it both expands adiabatically and evaporates
the cold shell surrounding it.  This hot, buoyant gas leaves the disc, rising
through the CGM and cooling adiabatically as it goes.  What is remarkable here
is just how similar the phase diagrams of these two galaxies are.  The slight
differences are what we would expect from Table~\ref{z0_table3}.  g19195 has
$\sim50\%$ less gas than g24334, and more than 3 times the SFR at $z=0$.  Thus,
there is less total material, especially in the warm and cold phases, and
slightly more of the very hot ($T>5\times10^7\K$) gas (the interiors of very young
superbubbles) as a consequence of the higher SFR.  What is important to take
away from these phase diagrams is that a well-regulated and unregulated galaxy
do not have any real difference in the phase behaviour of their gas.  There is
no runaway cooling, or failure of SN to generate hot gas:  what causes the
unregulated population to runaway is purely an effect of the outflow
effectiveness, which is set by the depth of the potential well.

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR3}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR3}}
    \label{SMHMR_time3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time3}.  This indicates that both stellar mass
    and central baryonic masses are rapidly increasing together.}
    \label{stellar_central_time3}
\end{figure}

@@

The relatively smooth change in the $M_*-M_{\rm central}$ relation, shown in
Fig.~\ref{stellar_central_time3}, shows that it is in fact the central baryon
mass that is more tightly correlated with the stellar mass than the total halo
mass (in galaxies regulated by SN feedback alone). In fact, it is likely that
some of the more massive galaxies in the well-regulated sample are on their way
to failing, but simply have not yet had enough time by $z=0$ to diverge
significantly from the observed SMHMR.  Once more than $\sim10^{11}\Msun$ of
baryons have accreted to the disc of a galaxy, SN alone appear to be unable to
halt the growth of stellar mass.  At this point, star formation efficiency of
the central disc begins to increase, from $\sim40$ to $\sim70$ per cent, resulting in
the differences seen in the two populations at $z=0$.  This accretion crisis, as
it continues to smaller scales, also explains the rotation profiles of the
unregulated population.  The overcollapse that results in runaway star formation
also builds a massive bulge, producing the peaked rotation curves seen in
Fig.~\ref{rotation_curve3}.

@@

Fig.~\ref{massloading_halo3} suggests exactly that.  The mass loadings appear
roughly constant, at $\eta\sim10$ for most of the mass-range for both
populations, but begin to fall at essentially the same mass, at what appears to
be the same rate.  An even tighter relation is seen in
Fig.~\ref{massloading_central3}, when the relation between the central baryon
mass, rather than just the halo mass, is examined. It appears that for the
$\eta-M_{\rm halo}$ and $\eta-M_{\rm central}$ relation, a broken power-law fit, as
defined below, describes both the regulated and unregulated population.
\begin{equation}
    \eta = 
    \begin{cases}
        \alpha M^\beta  & \quad \text{if } M < M_0 \\
        (\alpha M_0^{\beta-\gamma}) M^\gamma & \quad \text{if } M > M_0 \\
    \end{cases}
    \label{outflow_scaling3}
\end{equation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_central.eps}
    \caption[Mass loadings as a function of disc mass]{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/coldmassloading.eps}
    \caption[Outflow mass loading for cold and hot gas]{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading3}
\end{figure}

Using a simple non-linear least squares fit on the parameters $\alpha$,
$\beta$, $\gamma$, and $M_0$, we find that the most likely value for these
parameters are $\alpha=0.9\pm0.5$, $\beta=-0.01\pm0.06$, $\gamma=-1.3\pm0.1$,
$M_{0}=10^{10.0\pm0.1}$ for the $\eta-M_{\rm central}$ relation, and $\alpha=1\pm1$,
$\beta=0.0\pm0.1$, $\gamma=-1.8\pm0.2$, $M_{0}=10^{11.37\pm0.08}$ for the
$\eta-M_{\rm halo}$ relation.  A fit for both of the populations independently is
consistent with these values derived for the full set of MUGS2 galaxies.
Interestingly, {\it neither} of these slopes is consistent with simple energy
or momentum driven winds (although a single power-law fit does give a slope of
$\sim0.5\pm0.2$, consistent with an energy-driven scenario, albeit with a much
weaker fit).  These values are consistent, however, with the constraints derived
for the mass--metallicity relation and gas content in nearby galaxies derived by
\citet{Peeples2011} (namely, that $\alpha$ in the $\eta\propto v_c^{-\alpha}$
relation be steeper than 3).
